Msc Thesis Figures

### 2020-08-04 docs/msc_thesis_figures.Rmd
updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages({
  library(raster)
  library(sf)
  library(tidyverse)
  library(ggplot2)
  library(gganimate)
  library(transformr)
  library(animation)
  library(rasterVis)
  library(ggmap)
  library(gifski)
  library(gtools)
  library(fmsb)
  library(RColorBrewer)
  library(scales)
  library(ggradar)
  library(tidymodels)
  library(patchwork)
})

theme_set(theme_minimal())
theme_update(legend.position = c(0.85, 0.20),
             legend.box = "vertical",
             legend.background = element_blank(),
             legend.box.background = element_rect(colour = "black"),
             panel.border = element_rect(fill = NA),
             legend.title = element_text(size = 22),
             legend.text = element_text(size = 22),
             plot.title = element_text(size=22),
             plot.subtitle = element_text(size=22),
             axis.text.x = element_text(angle=65, vjust=0.6, size =22),
             axis.text.y = element_text(size =22),
             strip.text.x = element_text(size = 22),
             strip.text.y = element_text(22),
             axis.title=element_text(size=22))

source("../scripts/functions/draw_scenario.R")
```

@@

```{r eval=FALSE, include=FALSE}
class = 2

# LOAD
the_stack <- stack(lapply((list.files("../test/july/sce_37_for_urb_prob/", full.names = T)), raster)) == class

original <- raster("../data/land_use/aggregated/aggregated_lu_buffered_1990_patched.tif") == class
final <- raster("../data/land_use/aggregated/aggregated_lu_buffered_2010_patched.tif") == class
stratum <- raster("../data/stsim/aggregated/primary_stratum_mont_or_not_or_PA.tif")

@@

# Fill th "other" values
the_mean[(which(values(!is.na(final)) & values(is.na(the_mean))))] <- 0

@@

aucs <- c()
precs <- c()
for (x in 1:nlayers(the_stack)){
  the_df <- as.data.frame(stack(the_stack[[x]], final)) %>% 
    drop_na() %>% 
    rename(estimate = starts_with("model"), truth = "observation")
  the_df_2 <- the_df %>% 
    mutate(truth = factor(truth, ordered = F)) %>%
    mutate(truth = relevel(.$truth, "1"))
  auc <- the_df_2 %>% 
    roc_auc(truth = truth, estimate) %>% 
    pull(.estimate)
  prec <- the_df_2 %>% 
    average_precision(truth = truth, estimate) %>% 
    pull(.estimate)
  aucs <- c(aucs, auc)
  precs <- c(precs, prec)
}
mean(aucs);sd(aucs)
mean(precs);sd(precs)
# plot(stack(the_mean, final))
```

@@

```{r BAU, eval=FALSE, include=FALSE, message=FALSE, warning=FALSE}
# draw_scenario(39)
final_df_39 <- draw_scenario(39, return_df = T)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages({
  library(raster)
  library(sf)
  library(tidyverse)
  library(ggplot2)
  library(gganimate)
  library(transformr)
  library(animation)
  library(rasterVis)
  library(ggmap)
  library(gifski)
  library(gtools)
  library(fmsb)
  library(RColorBrewer)
  library(scales)
  library(ggradar)
  library(tidymodels)
  library(patchwork)
  library(ggplotify)
})

theme_set(theme_minimal())
theme_update(legend.position = c(0.85, 0.20),
             legend.box = "vertical",
             legend.background = element_blank(),
             legend.box.background = element_rect(colour = "black"),
             panel.border = element_rect(fill = NA),
             legend.title = element_text(size = 22),
             legend.text = element_text(size = 22),
             plot.title = element_text(size=22),
             plot.subtitle = element_text(size=22),
             axis.text.x = element_text(angle=65, vjust=0.6, size =22),
             axis.text.y = element_text(size =22),
             strip.text.x = element_text(size = 22),
             strip.text.y = element_text(22),
             axis.title=element_text(size=22))
```

@@

No outputs for github page

```{r 2010_compare_prep, include=FALSE}
list_of_files <-  list.files("../libraries/stsim/monteregie-conncons-scripted.ssim.output/Scenario-37/stsim_OutputSpatialState", full.names = T)
list_of_files <- list_of_files[grep(x=list_of_files, "ts2")]
stratum <- raster("../data/stsim/aggregated/primary_stratum_mont_or_not_or_PA.tif")
```

```{r 2010_compare_urb, include=FALSE}
names <- paste0(c("historic_compare_agex", "historic_compare_urb"), ".png")

for (class in c(1:2)){

  the_stack <- stack(lapply(list_of_files, raster)) == class
  original <- raster("../data/land_use/aggregated/aggregated_lu_buffered_1990_patched.tif") == class
final <- raster("../data/land_use/aggregated/aggregated_lu_buffered_2010_patched.tif") == class

@@

  # Fill the "other" values
  the_mean[(which(values(!is.na(final)) & values(is.na(the_mean))))] <- 0

  stack_to_plot <- stack(the_mean, final) 
  names(stack_to_plot) <- c("Model", "Observations")

  mxp <- 1e1000 # 10000

  myPal <- RColorBrewer::brewer.pal('OrRd', n=9)
  myTheme <- rasterTheme(region = myPal)
  probs <- levelplot(stack_to_plot$Model, scales=list(draw=FALSE),
                     maxpixels = mxp, 
                     par.settings = myTheme,
                     margin=FALSE, auto.key=FALSE, 
                     colorkey=list(space="bottom"), 
                     main = "A)")
  probs <- as.ggplot(probs)

  stack_to_plot$Observations <- ratify(stack_to_plot$Observations)
  rat <- levels(stack_to_plot$Observations)[[1]]
  rat$Urbanised <- c("Not Observed", "Observed")
  levels(stack_to_plot$Observations) <- rat
  bin <- levelplot(stack_to_plot$Observations, col.regions=c('grey', 'indianred4'), 
                   scales=list(draw=FALSE), 
                   maxpixels = mxp, 
                   colorkey=list(space="bottom", height=0.3), 
                   main = "B)")
  bin <- as.ggplot(bin)

  final_plot <- probs + bin

  ggsave(plot = final_plot, filename = paste0("../thesis/figures/",names[class]), width = the_width, height = the_height, dpi = the_dpi)
}
```

<!--
```{r eval=FALSE, include=FALSE}

@@

aucs <- c()
precs <- c()
for (x in 1:nlayers(the_stack)){
the_df <- as.data.frame(stack(the_stack[[x]], final)) %>% 
drop_na() %>% 
rename(estimate = starts_with("model"), truth = "observation")
the_df_2 <- the_df %>% 
mutate(truth = factor(truth, ordered = F)) %>%
mutate(truth = relevel(.$truth, "1"))
auc <- the_df_2 %>% 
roc_auc(truth = truth, estimate) %>% 
pull(.estimate)
prec <- the_df_2 %>% 
average_precision(truth = truth, estimate) %>% 
pull(.estimate)
aucs <- c(aucs, auc)
precs <- c(precs, prec)
}
mean(aucs);sd(aucs)
mean(precs);sd(precs)
```
-->

@@

```{r BAU, eval=FALSE, include=FALSE, message=FALSE, warning=FALSE}
the_folder <- "../test/july/all/monteregie-conncons-scripted.ssim.output"
# draw_scenario(39)
final_df_39 <- draw_scenario(sce = 39, return_df = T, sce_folder=the_folder)
